### 2016-02-22 text/ms.Rmd
Edits to text for revision

@@

@@

\noindent
Running head: Superensembles of population status

@@

\bigskip
\noindent
\textbf{Abstract:} Ecological resource managers must often reconcile multiple conflicting estimates of population status and trend. One solution is to average these predictions in an ensemble, but this approach ignores covariance between models and may not optimally reduce bias and improve accuracy. Superensemble models, commonly used in climate and weather forecasting, may provide a superior solution. Superensembles use the predictions from multiple models as covariates in an additional statistical model fit to known data. Here we evaluate the potential for ensemble and superensemble models ('ensemble methods') to improve estimates of fish population status and trend. We fit four data-limited and widely applicable models of population and exploitation dynamics and combine the models' estimates of the mean and recent trend in biomass relative to the equilibrium biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with an ensemble average and three superensembles: a linear model, a random forest, and a boosted regression tree. We built our models on a simulated dataset of 5760 stocks and tested them with cross-validation and against a global database of `r ram_stocks_n` stock assessments. We found that ensemble methods substantially improved estimates of population status and trend. Machine-learning superensembles (random forest and boosted regression trees) performed the best for estimating population status: accuracy improved `r mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted and true status improved from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median proportional error) declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We found similar improvements when predicting the trend of status and when applying the simulation-trained superensembles to catch data for global fish stocks. Ensemble methods have the potential to improve estimates of population status and trends for a wide variety of plant and animal species. However, they must be tested, formed from a diverse set of accurate models, and built on a dataset representative of the populations to which they are applied.

@@

Population status and trend are two of the most fundamental values to quantify in conservation biology [e.g. @mace2008; @iucn2015]. These properties are key to everything from global assessments of extinction risk [e.g. @stuart2004; @schipper2008] to assessing the sustainability of hunting [e.g. @fa2002] and fishing exploitation levels [e.g. @worm2009; @juan-jorda2011]. However, conservation and ecological resource managers are often faced with reconciling multiple uncertain and potentially conflicting estimates of status and trend [e.g. @brodziak2010; @branch2011; @deroba2015]. Some models may suggest a population is at risk and declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of an ensemble of model predictions. Such ensembles are typically more accurate and less biased than individual model estimates and can integrate uncertainty in model structure, initial conditions, and parameter estimation [@dietterich2000; @araujo2007]. This approach forms the basis of many machine learning methods [e.g. @dietterich2000], has helped reconcile climate forecasts from dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are frequently used to improve species distribution modelling [e.g. @araujo2007; @breiner2015] and indeed have been used to combine estimates of population status and trend [e.g. @brodziak2010].

@@

Here, we estimate population status and trend of exploited fish populations using ensembles and superensembles (collectively 'ensemble methods') of these four data-limited models. We apply four ensemble-method approaches of increasing complexity to both simulated and real-world fish stocks and compare their predictive performance against each other and the individual models.

@@

We first developed and tested ensemble methods on a fully factorial simulated dataset [@rosenberg2014] with known status. These published simulated data included the following scenarios: three fish life histories: small pelagic, demersal, and large pelagic; three levels of initial biomass depletion compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying capacity; and four exploitation settings: (1) a constant exploitation rate, (2) an exploitation rate coupled with biomass to mimic an open-access single-species fishery, (3) a scenario where exploitation rate increased continuously, and (4) a 'roller-coaster' scenario where the exploitation rate increased and then decreased. Process noise (recruitment variability; i.e. unexplained variability in population dynamics) was introduced to the models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$, and was either uncorrelated through time or had a first-order autoregressive correlation of $0.6$. The simulation also included a scenario with $N(0, 0.2^2)$ measurement error around log(catch) and one scenario without measurement error.
@rosenberg2014 ran ten iterations for each combination of factors adding stochastic draws of recruitment and catch-recording variability each time to generate a total of 5760 stocks.

<!--TODO add back when identity public: The simulation models were built in the package `FLR` [@kell2007, <http://flr-project.org>] for the statistical software \textsf{R} [@r2015]. -->
<!--Code to generate the simulations is available at <https://github.com/iagomosqueira/stockStatusFAO>.-->

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database [@ricard2012] --- a compilation of stock-assessment output from hundreds of exploited marine populations around the world. Our analysis of the stock-assessment database was based on version 2.5; after removing stocks for which at least one of the individual models described below did not converge (121), this database included `r ram_stocks_n` stocks.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year, $B_t$ represents biomass at time $t$, $r$ represents the intrinsic population growth rate, $B_0$ represents unfished biomass or carrying capacity $K$, and $C$ represents catch. The fourth model is an empirically derived model based on the RAM Legacy Stock Assessment Database. @rosenberg2014 provide a full background on these four methods and code to fit the models. In summary:

<!--and code to fit all the models is available in an accompanying package `datalimited` (TODO: make public?) for the statistical software \textsf{R}. In summary:-->

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer biomass dynamics [@martell2013]. It requires a prior distribution for $r$ and assigns a prior to the relative proportion of biomass at the end of the time series compared to unfished biomass (depletion) based on the percentage of maximum catch at the end of the time series. The version of the model used in @rosenberg2014 was modified from @martell2013 to generate biomass trends from all viable $r$-$K$ pairs and produce an estimate of $B/B_\mathrm{MSY}$ from the median trend.

* *COM-SIR* (catch-only-model with sampling-importance-resampling) is a coupled harvest-dynamics model [@vasconcellos2005]. Biomass is assumed to follow a Schaefer model and harvest dynamics are assumed to follow a logistic model. The model is fit with a sampling-importance-sampling algorithm [@rosenberg2014].

@@

<!--TODO Kristin and Mark: It might be a good idea to add a figure that illustrates the spectrum of ensemble/superensembles that are applied here and what is included (e.g., non-linear relationships, etc.). This will help the reader understand the progression in complexity of the ensemble approaches I think.-->
Superensemble models allow us to incorporate additional covariates and potentially leverage interactions between these covariates and individual model predictions. Additional covariates could be, for example, life-history characteristics, information on exploitation patterns, or statistical properties of the data. For simplicity, and since many possible covariates, such as fishing effort dynamics, would not be known for many real-world data-limited scenarios, we added only one set of additional covariates: spectral properties of the catch time series. Spectral analysis decomposes a time series into the frequency domain and provides a means of describing the cyclical shape of the catch series that is independent of time series length (except in affecting precision) and absolute magnitude of catch. We fit spectral models to the scaled catch time series (catch divided by maximum catch) with the `spec.ar` function in \textsf{R} and recorded representative short- and long-term spectral densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year cycles.

@@

The individual models we seek to combine with superensembles provide time series of stock status ($B/B_\mathrm{MSY}$). Therefore, we can use superensembles to estimate multiple properties of these time series. Here, we focus on two properties: the mean and slope of $B/B_\mathrm{MSY}$ in the last 5 years. Together, these quantities address the recent state and trend of stock status, which are both of management and conservation interest [e.g. @mace2008]. To avoid undue influence of the end points of the time series on the calculated slope, we measured the slope as the Theil-Sen estimator of median slope [@theil1950].

We used the mean or slope of $B/B_\mathrm{MSY}$ as the response and the predictions from the individual models, and the spectral values, as predictors in our superensemble models. When modelling mean $B/B_\mathrm{MSY}$ --- a ratio bounded at zero --- we fit the superensemble models in log space and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, which are not bounded at zero, we fit superensemble models on the natural untransformed scale.

We compared an ensemble average and three superensembles of varying complexity: a linear model with two-way interactions, a random forest, and a boosted regression tree. We fit the linear model superensemble with all second-order interactions. Our two machine learning superensemble models, a random forest and a boosted regression tree, were based on regression trees. Regression trees sequentially determine what value of a predictor best splits the response data into two 'branches' based on a loss function [@breiman1984]. In random forests, a series of regression trees are built on a random subset of the data and random subset of the covariates of the model [@breiman2001]. In generalized boosted models (GBMs), each subsequent model is fit to the residuals from the previous model; data points that are fit poorly in a given model are given more weight in the next model [@elith2008]. Random forests and GBMs can provide strong predictive performance and fit highly non-linear relationships [@elith2008; @hastie2009]. We fit random forest models with the `randomForest` package [@liaw2002] for \textsf{R} with the default argument values. We fit boosted regression tree models with the `gbm` package [@ridgeway2015] for \textsf{R}. Based on initial tuning with the **caret** \textsf{R} package [@caret2008], we chose to fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate (shrinkage parameter) of $0.01$, and all other arguments at their default values.

@@

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/\abs{b}$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. When cross-validating against the RAM Legacy Stock Assessment database, we treated the estimates from these data-rich stock assessments as known without error. Thus, any error in the stock-assessment estimates of the mean or slope of $B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for each of the four data-limited models and the ensembles. We measured the ability for each model to correctly place stocks into categories of above or below $B/B_\mathrm{MSY} = 0.5$ at any decision threshold by plotting receiver operating characteristic curves; a threshold of $B/B_\mathrm{MSY} = 0.5$ is used to classify a stock as overfished in Australia and the United States [@daff2007; @hilborn2010]. Code to reproduce our analysis and an \textsf{R} package to fit the data-limited assessment models are available at <https://github.com/...> (*Private while in review*).

@@

The superensemble models were able to improve the predictive performance by harnessing the best properties of individual models, the covariance between individual models, and interactions with other covariates. For example, SSCOM had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig. \ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited the covariance between individual model predictions. For instance, both the linear model and GBM ensemble suggest that if mPRM and SSCOM predict high status, the true status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The addition of spectral density covariates helped the superensemble models correctly predict higher status values (Fig. \ref{hexagon}g, h) due to the interactions between the spectral density predictors and the individual model predictors (Fig. \ref{partial-2d-sim}). Although the additional covariates improved ensemble fit, performance of the ensembles was only marginally degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig. \ref{hexagon-sim-basic}).

@@

Multi-model inference in the form of coefficient averaging weighted by information theoretics such as the Akaike Information Criterion (AIC) is a common analytical approach in ecology [@burnham2002; @johnson2004; @grueber2011]. The ensemble methods described in this paper share similarities with coefficient averaging but differ in other important ways. Ensemble methods and coefficient averaging share the long-held notion that multiple working hypotheses can contribute useful information for inference [@chamberlin1890]. A fundamental difference is that coefficient averaging focuses on averaging *coefficients* whereas ensembles instead average *predictions*. Thus, while the outcome will be the same in some cases, ensembles provide a more general purpose tool: they do not require information theoretics and they can combine different types of models (e.g. parametric and non-parametric models or frequentist and Bayesian predictions). Furthermore, superensembles extend these benefits by allowing model predictions to be combined via non-linear functions that are tuned to known data.

>>>>

<!-- TODO
- [ ] trash slope?
- [ ] trash covariates?
- [ ] add discussion of uncertainty (CIs) and ML (and incorporating uncertainty into pred.)
- [ ] add table of fish methods and ensemble models
- [ ] add flow chart of cross validation / methods
-->

@@

\noindent
Alternative 1: Combining stock-assessment output with ensemble modelling

\noindent
Alternative 2: Ensembles of data-limited stock-assessments can improve accuracy and reduce bias of $B/B_\mathrm{MSY}$ estimates

@@

\noindent
Running title: Superensembles of population status

@@

\bigskip
\noindent
\textbf{Abstract:} Fishery managers must often reconcile conflicting estimates of population status and trend. One solution is to average predictions in an ensemble, but this approach ignores covariance between models and may not optimally reduce bias and improve accuracy. Superensemble models, commonly used in climate and weather forecasting, may provide a superior solution. Superensembles use predictions from multiple models as covariates in an additional model fit to known data. We evaluated the potential for ensemble and superensemble models ('ensemble methods') to improve estimates of population status and trend. We fit four data-limited and widely applicable models of population and exploitation dynamics and combined the models' estimates of the mean and recent trend in biomass relative to the equilibrium biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$) with an ensemble average and three superensembles: a linear model, a random forest, and a boosted regression tree. We built our models on a simulated dataset of 5760 stocks and tested them with cross-validation and against a database of `r ram_stocks_n` stock assessments. We found that ensemble methods substantially improved estimates of population status and trend. Random forest and boosted regression trees performed the best for estimating population status: accuracy improved `r mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted and true status improved from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median proportional error) declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We found similar improvements when predicting the trend of status and when applying the simulation-trained superensembles to catch data for global fish stocks. Ensemble methods can improve estimates of status and trends; however, they must be tested, formed from a diverse set of accurate models, and built on a dataset representative of the populations to which they are applied. *TODO: Still need to cut ~30 words*

@@

Population status and trend are two of the most fundamental values to quantify in fisheries management [e.g. TODO NEW REFS]. However, fisheries managers are often faced with reconciling multiple uncertain and potentially conflicting estimates of status and trend [e.g. @brodziak2010; @branch2011; @deroba2015]. Some models may suggest a population is at risk and declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of an ensemble of model predictions. Such ensembles are typically more accurate and less biased than individual model estimates and can integrate uncertainty in model structure, initial conditions, and parameter estimation [@dietterich2000; @araujo2007]. This approach forms the basis of many machine learning methods [e.g. @dietterich2000], has helped reconcile climate forecasts from dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even improved early warning signs of malaria outbreaks [@thomson2006]. In ecology, ensemble methods are sometimes used to improve species distribution modelling [e.g. @araujo2007; @breiner2015] and indeed have been used to combine estimates of population status and trend [e.g. @brodziak2010].

@@

Here, we estimate population status and trend of exploited fish populations using ensembles and superensembles (collectively 'ensemble methods') of these four data-limited models. We apply four ensemble-method approaches of varying complexity to both simulated and real-world fish stocks and compare their predictive performance against each other and the individual models.

@@

We first developed and tested ensemble methods on a fully factorial simulated dataset [@rosenberg2014] with known status. These published simulated data included the following scenarios: three fish life histories: small pelagic, demersal, and large pelagic; three levels of initial biomass depletion compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying capacity; and four exploitation settings: (1) a constant exploitation rate, (2) an exploitation rate coupled with biomass to mimic an open-access single-species fishery, (3) a scenario where exploitation rate increased continuously, and (4) a 'roller-coaster' scenario where the exploitation rate increased and then decreased. Process noise (recruitment variability; i.e. unexplained variability in population dynamics) was introduced to the models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$, and was either uncorrelated through time or had first-order autoregressive correlation of $0.6$. The simulation also included a scenario with $N(0, 0.2^2)$ measurement error around log(catch) and one scenario without measurement error. @rosenberg2014 ran ten iterations for each combination of factors adding stochastic draws of recruitment and catch-recording variability each time to generate a total of 5760 stocks. 
The simulation models were built in the package `FLR` [@kell2007, <http://flr-project.org>] for the statistical software R [@r2015].
Code to generate the simulations is available at <https://github.com/iagomosqueira/stockStatusFAO>.

We also tested our ensemble methods on the RAM Legacy Stock Assessment Database [@ricard2012] --- a compilation of stock-assessment output from hundreds of exploited marine populations around the world. Our analysis of the stock-assessment database was based on version 2.5. After removing stocks for which at least one of the individual models described below did not converge (121), this database included `r ram_stocks_n` stocks.

@@

\noindent
where $\hat{B}_{t+1}$ represents predicted biomass at time $t$ plus one year, $B_t$ represents biomass at time $t$, $r$ represents the intrinsic population growth rate, $B_0$ represents unfished biomass or carrying capacity $K$, and $C$ represents catch. The fourth model is an empirically derived model based on the RAM Legacy Stock Assessment Database. @rosenberg2014 provide a full background on these four methods 
and code to fit all the models is available in an accompanying package `datalimited` for the statistical software R TODO ADD URL. In summary:

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer biomass dynamics [@martell2013]. It requires a prior distribution for $r$ and a prior on the relative proportion of biomass at the end of the time series compared to unfished biomass (depletion), which is derived from the percentage of maximum catch at the end of the time series. The version of the model used in @rosenberg2014 was modified from @martell2013 to generate biomass trends from all viable $r$-$K$ pairs and produce an estimate of $B/B_\mathrm{MSY}$ from the median trend.

* *COM-SIR* (catch-only-model with sampling-importance-resampling) is a coupled harvest-dynamics model [@vasconcellos2005]. Biomass is assumed to follow a Schaefer model and harvest dynamics are assumed to follow a logistic model. The model is fit with a sampling-importance-resampling algorithm [@rosenberg2014].

@@

<!--TODO Kristin and Mark: It might be a good idea to add a figure that illustrates the spectrum of ensemble/superensembles that are applied here and what is included (e.g., non-linear relationships, etc.). This will help the reader understand the progression in complexity of the ensemble approaches I think.-->
<!-- TODO deal with removed spectral -->
<!-- 
Superensemble models allow us to incorporate additional covariates and potentially leverage interactions between these covariates and individual model predictions. Additional covariates could be, for example, life-history characteristics, information on exploitation patterns, or statistical properties of the data. For simplicity, and since many possible covariates, such as fishing effort dynamics, would not be known for many real-world data-limited scenarios, we added only one set of additional covariates: spectral properties of the catch time series. Spectral analysis decomposes a time series into the frequency domain and provides a means of describing the cyclical shape of the catch series that is independent of time series length (except in affecting precision) and absolute magnitude of catch. We fit spectral models to the scaled catch time series (catch divided by maximum catch) with the `spec.ar` function in R and recorded representative short- and long-term spectral densities at frequencies of 0.20 and 0.05, which correspond to 5- and 20-year cycles.
-->

@@

The individual models we seek to combine with superensembles provide time series of stock status ($B/B_\mathrm{MSY}$). Therefore, we can use superensembles to estimate any property of these time series. Here, we focus on two properties: the mean and slope of $B/B_\mathrm{MSY}$ in the last five years. Together, these quantities address the recent state and trend of stock status, which are both of management and conservation interest [e.g. @mace2008] TODO add fishery REF. To avoid undue influence of the end points of the time series on the calculated slope, we measured the slope as the Theil-Sen estimator of median slope [@theil1950].

We used the mean or slope of $B/B_\mathrm{MSY}$ as the response and the predictions from the individual models
<!--, and the spectral values, -->
as predictors in our superensemble models. When modelling mean $B/B_\mathrm{MSY}$ --- a ratio bounded at zero --- we fit the superensemble models in log space and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, which are not bounded at zero, we fit superensemble models on the natural untransformed scale.

We compared an ensemble average and three superensembles of varying complexity: a linear model with two-way interactions, a random forest, and a boosted regression tree. We describe these models as estimating $\hat{\theta}$, which represents either 
the ensemble estimated $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$. The individual model estimates of $\log B/B_\mathrm{MSY}$ or slope of $B/B_\mathrm{MSY}$ are represented as $b$ for models $i$ $1$ through $n$ ($4$). The ensemble average was calculated as:

\begin{equation} 
\hat{\theta} = \frac{1}{n} \sum_{i=1}^n \hat{b_i}.
\end{equation}

$$ \hat{\theta} = \argmin_\theta \left( L(b \, | \, \hat{b}{\mathrm{ensemble}}) \right) $$ $$ \hat{b}\mathrm{ensemble} = f \left( \hat{b}\mathrm{CMSY}, \, \hat{b}\mathrm{COM-SIR}, \, \hat{b}\mathrm{SSCOM}, \, \hat{b}\mathrm{mPRM}, \, S(0.2), \, S(0.5), \, | \, \theta \right) $$

We fit the linear model superensemble with all second-order interactions:

\begin{equation} \theta_{\mathrm{ensemble}(i)} = \beta_0 + \sum_{j=1}^m \beta_j \theta_{j(i)} + \sum_{j=1}^m \sum_{\substack{k =1 \ j \neq k}}^m \beta_{kj} \theta_{k(i)} \theta_{j(i)} + \epsilon_i, \quad \epsilon_i \sim \mathrm{Normal}(0, \sigma), \end{equation}

TODO ADD EQN

Our two machine learning superensemble models, a random forest and a boosted regression tree, were based on regression trees. Regression trees sequentially determine what value of a predictor best splits the response data into two 'branches' based on a loss function [@breiman1984]. In random forests, a series of regression trees are built on a random subset of the data and random subset of the covariates of the model [@breiman2001]. In generalized boosted models (GBMs), each subsequent model is fit to the residuals from the previous model; data points that are fit poorly in a given model are given more weight in the next model [@elith2008]. Random forests and GBMs can provide strong predictive performance and fit highly non-linear relationships [@elith2008; @hastie2009]. We fit random forest models with the `randomForest` package [@liaw2002] for R with the default argument values. We fit boosted regression tree models with the `gbm` package [@ridgeway2015] for R. Based on initial tuning with the **caret** R package [@caret2008], we chose to fit GBMs with 2000 trees, an interaction depth of $6$, a learning rate (shrinkage parameter) of $0.01$, and all other arguments at their default values:

TODO ADD EQN

@@

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/\abs{b}$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. When cross-validating against the RAM Legacy Stock Assessment database, we treated the estimates from these data-rich stock assessments as known without error. Thus, any error in the stock-assessment estimates of the mean or slope of $B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for each of the four data-limited models and the ensembles. We measured the ability for each model to correctly place stocks into categories of above or below $B/B_\mathrm{MSY} = 0.5$ at any decision threshold by plotting receiver operating characteristic curves; a threshold of $B/B_\mathrm{MSY} = 0.5$ is used to classify a stock as overfished in Australia and the United States [@daff2007; @hilborn2010]. Code to reproduce our analysis and an R package to fit the data-limited assessment models are available at <https://github.com/datalimited/...> (*Private while in review*).

@@

The superensemble models were able to improve the predictive performance by harnessing the best properties of individual models, the covariance between individual models, and interactions with other covariates. For example, SSCOM had strong predictive ability when it predicted low $B/B_\mathrm{MSY}$ (Fig. \ref{hexagon}c, Fig. \ref{partial-sim}c) and CMSY predictions were approximately linearly related to $B/B_\mathrm{MSY}$ within the low and high clusters of predictions (Fig. \ref{partial-sim}). Superensembles also exploited the covariance between individual model predictions. For instance, both the linear model and GBM ensemble suggest that if mPRM and SSCOM predict high status, the true status also tends to be high (Figs \ref{lm-coefs}, \ref{partial-2d-sim}l). The addition of spectral density covariates helped the superensemble models correctly predict higher status values (Fig. \ref{hexagon}g, h) due to the interactions between the spectral density predictors and the individual model predictors (Fig. \ref{partial-2d-sim}). Although the additional covariates improved ensemble fit, performance of the ensembles was only marginally degraded by removing these covariates (Fig. \ref{hexagon} vs. Fig. \ref{hexagon-sim-basic}).
<!--TODO trash this?-->

@@

Multi-model inference in the form of coefficient averaging weighted by information theoretics such as the Akaike Information Criterion (AIC) is a common analytical approach in ecology [@burnham2002; @johnson2004; @grueber2011]. The ensemble methods described in this paper share similarities with coefficient averaging but differ in other important ways. Ensemble methods and coefficient averaging share the long-held notion that multiple working hypotheses can contribute useful information for inference [@chamberlin1890]. A fundamental difference is that coefficient averaging focuses on averaging *coefficients* whereas ensembles instead average *predictions*. Thus, ensembles provide a more general purpose tool: they do not require information theoretics and they can combine different types of models (e.g. parametric and non-parametric models or frequentist and Bayesian predictions). Furthermore, superensembles extend these benefits by allowing model predictions to be combined via non-linear functions that are tuned to known data.
